SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-24 docs/questioning.tex
changes in Section 4

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that counter web application attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it protection} and {\it detection}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.

\subsection{Protection}
\label{sec:prot}

@@

{\sc isr} is a method that contrary to the previous
two, has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.
The main idea behind the method, is to
separate code from data by randomizing the legitimate code's 
execution environment. In this way, the malicious code
injected by the attackers who do not know the randomization
algorithm, will not get executed.

@@

\subsection{Detection}

@@

>>>>

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that protect web applications against attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it design-based} and {\it behavior-based}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.

\subsection{Design-Based}
\label{sec:prot}

@@

{\sc isr} is a method that contrary to the previous
three, has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.
The main idea behind the method, is to
separate code from data by randomizing the legitimate code's 
execution environment. In this way, the malicious code
injected by the attackers who do not know the randomization
algorithm, will not get executed.

@@

\subsection{Behavior-Based}

@@

	\multirow{8}{*}{Runtime Tainting}
